% This is a template for lecture notes.
\documentclass[12pt]{article}
\usepackage{amssymb}
\usepackage[UTF8]{ctex}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{bm}
\usepackage{cite}
%\usepackage{CJK}
\usepackage[many]{tcolorbox}
%\tcbuselibrary{listingsutf8}
%\tcbuselibrary{skins, breakable, theorems, most}
%\geometry{a4paper,bottom = 3cm,left = 3cm, right = 3cm}
\CTEXoptions[today=old]
%for reference
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\crefname{enumi}{}{}


\newtheoremstyle{mythm}{1.5ex plus 1ex minus .2ex}{1.5ex plus 1ex minus .2ex} 
    {}{\parindent}{\bfseries}{}{1em}{} 
\theoremstyle{mythm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{remark}{Remark}

%\newenvironment{proof}{\noindent \textbf{Proof:}}{$\Box$}

%to use newcommand for convenience
\newcommand\field{\mathbb{F}}
\newcommand\Real{\mathbb{R}}
\newcommand\Q{\mathbb{Q}}
\newcommand\Z{\mathbb{Z}}
\newcommand\complex{\mathbb{C}}
\newcommand\cc{\mathcal{C}}
\newcommand\uu{\mathcal{U}}
\newcommand\pp{\mathcal{P}}
\newcommand\ff{\mathcal{F}}
\renewcommand\refname{Reference}
\renewcommand{\proofname}{Proof}
\DeclareMathOperator{\range}{range}   

\title{Construction of 4 sets to satisfy 3 rules}
\author{马浩博 518030910428}
\date{\today}
\begin{document}
\maketitle

\section*{Exercise 8}
\begin{tcolorbox}
  Construct three sets A, B, C and a set E $\subseteq$ $A \times B \times C$ 
  such that the following hold: 1) For every (a, b, c) $\in$ $A \times B \times C$, E has a matching which saturates {a, b, c}; 
  2) E has an (A∪B)-saturated matching, a (B∪C)-saturated matching, and an (A∪C)-saturated matching; 3) E does not have any (A∪B∪C)-saturated matching.

\end{tcolorbox}

\begin{proof}[Answer]

  Let me first give out the construction:
  $$A = \{1, 0, 4, 7 \}$$
  $$B = \{2, 0, 4, 7 \}$$
  $$C = \{3, 0, 4, 7 \}$$
  $$E = \bigcup\limits_{i=0}^5 \{e_i\}$$
  $$e_0 = (1,7,4)$$
  $$e_1 = (4,2,7)$$
  $$e_2 = (7,4,3)$$
  $$e_3 = (0,7,4)$$
  $$e_4 = (4,0,7)$$
  $$e_5 = (7,4,0)$$



  First, we shall prove it satisfies 3). Assume there is such matching $E'$. 
  Then $e_0$, $e_1$, $e_2$ must belong to $E'$ because only they have the elements 1,2,3. 
  Then we know $e_3 \notin E'$ because it's not disjoint with $e_0$, and same as $e_4, e_5$. 
  Thus there it no element which can cover 0. So such $E'$ doesn't exist.\\

  Next, we shall prove it satisfies 2). For $A \cup B$, we just need to let $\{e_0,e_1,e_5\}$ be the matching. 
  Beause of symmetry, we can know there are also $(B \cup C)$-saturated matching and $(C \cup A)$-saturated matching.\\

  Finally, we need to prove 1). If the $a$ in the choosen $(a,b,c)$ doesn't equal to 1, then we can just use the $(B \cup C)$-saturated matching.
  Same way if $b \neq 2$ or $c \neq 3$. So we just need to concern $(1,2,3)$. 
  To saturate this, we can use the macthing $\{e_0,e_1,e_2\}$.\\

  Hence, the construction is right. I thought for a long time and tried many constructions. 
  This should be the most concise one.

\end{proof}

\end{document}
